A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-23 tex/body.tex
more

\def\ackname{Acknowledgment}
\ourparagraph{\ackname.}
We owe a great debt to the development team of CVC4,
including Clark Barrett and Cesare Tinelli,
and in particular Morgan Deters,
who jointly with the first author developed the initial version
of the theory solver for datatypes in CVC4.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatypes or at least benevolently tolerated it, both of which we are thankful
for.
%
Peter Gammie and Andreas Lochbihler shared their private
theories with us so we could include them in the benchmarks.
Andrei Popescu helped clarify our thoughts regarding the axiomatization of
codatatypes and indicated related work. Dmitriy Traytel took part in discussions
about degenerate codatatypes.
%
Pascal Fontaine, Andreas Lochbihler, Mark Summerfield, and Dmitriy Traytel
suggested several textual improvements. The second author's research was
partially supported by the Deutsche Forschungs\-gemein\-schaft (DFG) project
\relax{Hardening the Hammer} (grant Ni\,491\slash 14-1).

>>>>

\def\ackname{Acknowledgment}
\ourparagraph{\ackname.}
We owe a great debt to the development team of CVC4,
including Clark Barrett and Cesare Tinelli,
and in particular Morgan Deters,
who jointly with the first author developed the initial version
of the theory solver for datatypes in CVC4.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatypes or at least benevolently tolerated it, both of which we are thankful
for.
%
Peter Gammie and Andreas Lochbihler shared their private
theories with us so we could include them in the benchmarks.
Andrei Popescu helped clarify our thoughts regarding the axiomatization of
codatatypes and indicated related work. Dmitriy Traytel took part in discussions
about degenerate codatatypes.
%
Pascal Fontaine, Andreas Lochbihler, Christophe Ringeissen, Mark Summerfield,
and Dmitriy Traytel suggested several textual improvements. The second author's
research was partially supported by the Deutsche Forschungs\-gemein\-schaft
(DFG) project \relax{Hardening the Hammer} (grant Ni\,491\slash 14-1).
